The not so widening achievement gap: an interntational comparison of the evolution of the SES achievement gap from 2000-2015

### 2017-08-18 paper/paper.Rnw
Trivial commit

results_math <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.25, 0.75))
results_read <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.25, 0.75))
results_math_topmid <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.5, 0.75))
results_read_topmid <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.5, 0.75))
results_math_midbottom <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.25, 0.5))
results_read_midbottom <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.25, 0.5))

# results_math <- read_rds("./paper/data/delete.Rdata")
# results_read <- read_rds("./paper/data/delete_read.Rdata")
# results_math_topmid <- read_rds("./paper/data/delete_math_topmid.Rdata")
# results_read_topmid <- read_rds("./paper/data/delete_read_topmid.Rdata")
# results_math_midbottom <- read_rds("./paper/data/delete_math_midbottom.Rdata")
# results_read_midbottom <- read_rds("./paper/data/delete_read_midbottom.Rdata")
# US is missing for reading

@@

\begin{figure}
\begin{center}
<<graphing_9010gaps, include = T, out.height = '5in', out.width = '5.5in', fig.align = 'center'>>=
# 90/10 gaps acros countries

@@

complete_data_topbottom %>%
  mutate(country = factor(country, levels = ordered_cnt, ordered = TRUE)) %>%
  filter(type_test == "read", !is.na(country)) %>%
  ggplot(aes(as.character(wave), difference)) +
  geom_point() +
  geom_linerange(aes(ymin = 0, ymax = difference))+
  geom_line(stat = "smooth", method = "lm", aes(group = 1),
            formula = y ~ splines::ns(x, 2), size = 0.7,
            colour = "red") +
  facet_wrap(~ country, ncol = 5) +
  scale_y_continuous(name = "90/10 gap in SD", expand = c(0, 0), lim = c(0, 3)) +
  scale_x_discrete(name = NULL, breaks = c(2000, 2009, 2015)) +
  ggthemes::theme_few() +
  theme(panel.spacing = unit(1, "lines"),
        panel.grid.major.y = element_line(colour = "grey")) +
  ggtitle("Evolution of the 90/10 achievement gap")
@
\caption{Evolution of the achievement gap for selected countries}
\end{center}
\end{figure}

>>>>

# results_math <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.25, 0.75))
# results_read <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.25, 0.75))
# results_math_topmid <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.5, 0.75))
# results_read_topmid <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.5, 0.75))
# results_math_midbottom <- test_diff(adapted_year_data, reliability_pisa, "MATH", c(0.25, 0.5))
# results_read_midbottom <- test_diff(adapted_year_data, reliability_pisa, "READ", c(0.25, 0.5))

# results_math_75 <- results_math
# results_read_75 <- results_read
# results_math_topmid_75 <- results_math_topmid
# results_read_topmid_75 <- results_read_topmid
# results_math_midbottom_75 <- results_math_midbottom
# results_read_midbottom_75 <- results_read_midbottom

results_math <- read_rds("./paper/data/delete.Rdata")
results_read <- read_rds("./paper/data/delete_read.Rdata")
results_math_topmid <- read_rds("./paper/data/delete_math_topmid.Rdata")
results_read_topmid <- read_rds("./paper/data/delete_read_topmid.Rdata")
results_math_midbottom <- read_rds("./paper/data/delete_math_midbottom.Rdata")
results_read_midbottom <- read_rds("./paper/data/delete_read_midbottom.Rdata")
# US is missing for reading

@@

\begin{figure}
\begin{center}
<<graphing_9010gaps, include = T, out.height = '5in', out.width = '5.5in', fig.align = 'center'>>=
# 90/10 gaps across countries

@@

p <- 
  complete_data_topbottom %>%
  mutate(country = factor(country, levels = ordered_cnt, ordered = TRUE)) %>%
  filter(type_test == "math", !is.na(country)) %>%
  ggplot(aes(as.character(wave), difference)) +
  geom_point() +
  facet_wrap(~ country, ncol = 5) +
  geom_linerange(aes(ymin = 0, ymax = difference))

p + geom_line(data = complete_data_topbottom %>%
                mutate(country = factor(country, levels = ordered_cnt, ordered = TRUE)) %>%
                filter(!is.na(country)),
              stat = "smooth", method = "lm", aes(group = 1),
              formula = y ~ splines::ns(x, 2), size = 0.7,
              colour = "red") +
  scale_y_continuous(name = "90/10 gap in SD", expand = c(0, 0), lim = c(0, 3)) +
  scale_x_discrete(name = NULL, breaks = c(2000, 2009, 2015)) +
  ggthemes::theme_few() +
  theme(panel.spacing = unit(1, "lines"),
        panel.grid.major.y = element_line(colour = "grey")) +
  ggtitle("Evolution of the 90/10 achievement gap")
@
\caption{Evolution of the achievement gap for selected countries}
\end{center}
\end{figure}
